Fast Hyperparameter Selection for Graph Kernels via Subsampling and\\Multiple Kernel Learning

### 2017-02-08 paper.tex
piccola correzione MKL
caratteristiche cpu inserite
compressione

\subsection{Multiple Kernel Learning}
\label{MKL}
MKL \cite{Gonen2011} is one of the most popular paradigms used to learn kernels in real world applications \cite{Bucak2014}. % Zien2007,Wang2015a,Sun
The kernels generated by these techniques are combinations of a prescribed set of basic kernels $\KK_1,...,\KK_R$ in the form:
$ \KK = \sum_{r=1}^R \eta_r \KK_r$ with $\eeta \in \Psi_q = \{ \eeta : \eeta \succcurlyeq 0, \| \eeta \|_q = 1 \}$. The value $q$ being the kind of mean used, is typically fixed to $1$ or $2$.

@@

@@

\tablename\ \ref{tab:res} shows the AUC score, standard deviation and computation time used to make kernels and models for all problems.

@@

@@

% ****************************************************************************
% BIBLIOGRAPHY AREA
% ****************************************************************************
%
\begin{footnotesize}
%
% IF YOU DO NOT USE BIBTEX, USE THE FOLLOWING SAMPLE SCHEME FOR THE REFERENCES
% ----------------------------------------------------------------------------

>>>>

\subsection{Multiple Kernel Learning}
\label{MKL}
MKL \cite{Gonen2011} is one of the most popular paradigms used to learn kernels in real world applications \cite{Bucak2014}. % Zien2007,Wang2015a,Sun
The kernels generated by these techniques are combinations of a prescribed set of basic kernels $\KK_1,...,\KK_R$ in the form:
$ \KK = \sum_{r=1}^R \eta_r \KK_r$ with $\eeta \in \{ \eeta : \eeta \succcurlyeq 0, \| \eeta \|_q = 1 \}$. The value $q$ being the kind of mean used, is typically fixed to $1$ or $2$.

@@

\vspace{-0.5cm}

@@

\tablename\ \ref{tab:res} shows the AUC score, standard deviation and computation time.\footnote{We used an Intel(R) Xeon(R) CPU E5-2680 2.70GHz, 256GB (RAM).}
 used to make kernels and models for all problems.

@@

\vspace{-0.15cm}

@@

% ****************************************************************************
% BIBLIOGRAPHY AREA
% ****************************************************************************
%
\vspace{-0.2cm}
\begin{footnotesize}
%
% IF YOU DO NOT USE BIBTEX, USE THE FOLLOWING SAMPLE SCHEME FOR THE REFERENCES
% ----------------------------------------------------------------------------
